### 2024-06-24 manuscript.tex
Add LTS figure

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/lts-dist.pdf}
\caption{
Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and
\textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from
the highest instantaneous temporal resolution data. Shown is also the chosen
dividing threshold of 12 K for `stable' and `unstable' conditions.
}
\label{fig:example}
\end{figure}
